### 2016-08-08 Engine.tex
添加:node merge(未完成)

As stated in the filter module, for a position $i$ of the text $T$, if
some pattern $p_j$ starts at $i$, there must be
$Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
$Hash[p_j[lss-k+1,k]]$ the \emph{signature} of $p_j$). This means that
we can group the patterns according to their signatures: patterns with
the same signature are grouped together to form a sub-pattern-set, and
for each sub-pattern-set we build a (small) AMT from it. In addition,
an index table is adopted to allow the corresponding AMT be retrieved
in $O(1)$ time by its signature. Now, the verification module is made
up of an index table and several small AMTs.

Particularly, once a suspicious position $i$ in $T$ is detected, the
value $Hash[T[i+lss-k,k]]$ is used as the index of the index table to
find the corresponding small AMT for verifying $i$. As the scale of
the AMT shr, the time for each verifying is reduced accordingly.

>>>>

As stated in the filter module, the filtering is based on the last
$k$-symbol block of the sliding window. In particular, for a position
$i$ of the text $T$, if some pattern $p_j$ starts at $i$, there must
be $Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
$Hash[p_j[lss-k+1,k]]$ the \emph{signature} of $p_j$). This means that
we can group the patterns according to their signatures: patterns with
the same signature are grouped together to form a sub-pattern-set, and
for each sub-pattern-set we build a (small) AMT. In addition, an index
table is adopted to allow the corresponding AMT be retrieved in $O(1)$
time by its signature. Now, the verification module is made up of an
index table as well as several small AMTs.

Particularly, once a suspicious position $i$ in $T$ is detected, the
value $Hash[T[i+lss-k,k]]$ is used as the index of the index table to
find the corresponding small AMT for verifying $i$. As the scale of
the AMT shrunk, the time for each verifying is reduced accordingly.

\subsubsection{Node Merge}
\label{sec:node merge}

The nodes in a path of AMT, each of which has only one key, can be
merged into one node. This technique can reduce both time and space
efficiency of the verification module. To illustrate this, consider
the pattern set $P={p_1=, p_2=,p_3=}$ and its corresponding AMT
constructed by the method presented in section . As shown in Fig , the
built AMT has three nodes, and each of nodes has only one key. This
AMT roughly takes bytes of memory ( bytes for the keys and 16 bytes
for the child pointers), however, if we combine the three nodes into
one, the keys will be merged into one string and the child pointers
are no long needed. The only issue needs to be addressed is to
distinguish the keys after they are merged.
